Assessing Usability of Tor Browser

### 2015-04-10 PETS2015-paper/paper.tex
Placeholder resources section.
abstract editing?
made a note in the abstract.

\begin{abstract}
Our talk will be about ongoing experiments aimed at
assessing and improving the usability of Tor Browser.
There have been been no major usability evaluations of
Tor Browser since the introduction of the 4.0 series,
which introduced radical UI changes.
We will briefly describe the results of a completed study
that examined downloading and installing the browser
and using it for basic browsing tasks.
This study uncovered a number of bugs and stopping points
and has already effected concrete change in the browser.
We will describe our plans for future studies aimed at
isolating specific browser features in depth,
with a detailed design of an experiment to evaluate
Tor Browser as a tool for censorship circumvention.
We solicit feedback on our experimental design
and the specific features of the browser that we are testing.
\end{abstract}

@@

What we hope to get from this experiment.

@@

>>>>

\begin{abstract}
Our talk will be about ongoing experiments aimed at
assessing and improving the usability of Tor Browser.
There have been been no major usability evaluations of
Tor Browser since the introduction of the 4.0 series,
which introduced radical UI changes.
We will briefly describe the results of a completed study
that examined downloading and installing the browser
and using it for basic browsing tasks.
This study uncovered a number of bugs and stopping points
and has already effected concrete change in the browser.
We will describe our plans for future studies aimed at
isolating specific browser features in depth,
with a detailed design of an experiment to evaluate
Tor Browser as a tool for censorship circumvention.
{\color {red}LL: I don't know how to say this, but I want the fact that we are evaluating it from a different standpoint --ie as a censorship circumvention tool, to stand out more. Also, we spend more abstract real estate talking about the first experiment rather than our design, which I think should be flipped. But for right now, I can't think of what exactly to fix so I'll look at this later.}
We solicit feedback on our experimental design
and the specific features of the browser that we are testing.
\end{abstract}

@@

What we hope to get from this experiment

@@

\section{Resources}

\url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}

\url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}

\url{https://people.torproject.org/~dcf/uxsprint2015/}
